Poseidon Adventure

### 2019-05-16 RethinkSamplingFunctions.Rmd
typo fix
add notes on weight disaggregation

So, lets try integrating `calc_stage2age` into `run_truth` as planned and we can compare the outputs to what we already have for the stage data. We will want to compare census biomass, survey biomass, length comps...
    + write another truth function that works on the Atlantis true age output?
    + load YOY file into run_truth (uses load_YOY function)
    + do we have to apply before calc_biomass_age, and sub output of calc_stage2age in for nums?
    + if so, how do we deal with the structn and resn portions?

>>>>

So, lets try integrating `calc_stage2age` into `run_truth` as planned and we can compare the outputs to what we already have for the stage data. We will want to compare census biomass, survey biomass, length comps...

    + write another truth function that works on the Atlantis true age output?
    + load YOY file into run_truth (uses load_YOY function)
    + do we have to apply before calc_biomass_age, and sub output of calc_stage2age in for nums?
    + if so, how do we deal with the structn and resn portions?

    May 16: Discussion with Isaac and Patrick: how to split weights to true age bins?
    + Simple interpolation? within a year or across years
    + Is Z calc lagged? doesnt look like it, simple within year Z like catch curve
    + Check whether there is a plus group in any Atlantis model--shouldn't be
    + First try a linear interpolation between weight groups
    + This may be more wrong for smallest fastest growing age classes
    + If so we can write something else for younger classes
    + Midpoint of weight for each age is the goal

### 2019-05-16 docs/index.Rmd
add notes on weight disaggregation

<a href="https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html" target="_blank">Big picture and new functions needed - May 10, 2019, updated May 15, 2019</a>

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html" target="_blank">Big picture and new functions needed - May 10, 2019, updated May 16, 2019</a>
